\item The Horizon Telescope Collaboration, , Akiyama, K., Albentosa-Ruíz, E., et al., incl.\ \textbf{Joshi, A. V.} 2025, \href{https://ui.adsabs.harvard.edu/abs/2025A\&A...693A.265E}{A\&A, 693, A265}\\\textit{The persistent shadow of the supermassive black hole of M87: II. Model comparisons and theoretical interpretations}

\item \textbf{Joshi, A. V.}, Prather, B. S., Chan, C., Wielgus, M., et al. 2024, \href{https://ui.adsabs.harvard.edu/abs/2024ApJ...972..135J}{ApJ, 972, 135}\\\textit{Circular Polarization of Simulated Images of Black Holes}

\item Event Horizon Telescope Collaboration, , Akiyama, K., Alberdi, A., et al., incl.\ \textbf{Joshi, A. V.} 2024, \href{https://ui.adsabs.harvard.edu/abs/2024ApJ...964L..26E}{ApJL, 964, L26}\\\textit{First Sagittarius A* Event Horizon Telescope Results. VIII. Physical Interpretation of the Polarized Ring}

\item Event Horizon Telescope Collaboration, , Akiyama, K., Alberdi, A., et al., incl.\ \textbf{Joshi, A. V.} 2023, \href{https://ui.adsabs.harvard.edu/abs/2023ApJ...957L..20E}{ApJL, 957, L20}\\\textit{First M87 Event Horizon Telescope Results. IX. Detection of Near-horizon Circular Polarization}

\item Conroy, N. S., Bauböck, M., Dhruv, V., et al., incl.\ \textbf{Joshi, A. V.} 2023, \href{https://ui.adsabs.harvard.edu/abs/2023ApJ...951...46C}{ApJ, 951, 46}\\\textit{Rotation in Event Horizon Telescope Movies}

\item \textbf{Joshi, A. V.}, Rosofsky, S. G., Haas, R., \& Huerta, E. A. 2023, \href{https://ui.adsabs.harvard.edu/abs/2023PhRvD.107f4038J}{PhRvD, 107, 064038}\\\textit{Numerical relativity higher order gravitational waveforms of eccentric, spinning, nonprecessing binary black hole mergers}

\item Event Horizon Telescope Collaboration, , Akiyama, K., Alberdi, A., et al., incl.\ \textbf{Joshi, A. V.} 2022, \href{https://ui.adsabs.harvard.edu/abs/2022ApJ...930L..12E}{ApJL, 930, L12}\\\textit{First Sagittarius A* Event Horizon Telescope Results. I. The Shadow of the Supermassive Black Hole in the Center of the Milky Way}

\item Event Horizon Telescope Collaboration, , Akiyama, K., Alberdi, A., et al., incl.\ \textbf{Joshi, A. V.} 2022, \href{https://ui.adsabs.harvard.edu/abs/2022ApJ...930L..16E}{ApJL, 930, L16}\\\textit{First Sagittarius A* Event Horizon Telescope Results. V. Testing Astrophysical Models of the Galactic Center Black Hole}

\item Wong, G. N., Prather, B. S., Dhruv, V., et al., incl.\ \textbf{Joshi, A. V.} 2022, \href{https://ui.adsabs.harvard.edu/abs/2022ApJS..259...64W}{ApJS, 259, 64}\\\textit{PATOKA\@: Simulating Electromagnetic Observables of Black Hole Accretion}

\item Marszewski, A., Prather, B. S., \textbf{Joshi, A. V.}, Pandya, A., et al. 2021, \href{https://ui.adsabs.harvard.edu/abs/2021ApJ...921...17M}{ApJ, 921, 17}\\\textit{Updated Transfer Coefficients for Magnetized Plasmas}

\item Pandya, A., Chandra, M., \textbf{Joshi, A. V.}, \& Gammie, C. F. 2018, \href{https://ui.adsabs.harvard.edu/abs/2018ApJ...868...13P}{ApJ, 868, 13}\\\textit{Numerical Evaluation of the Relativistic Magnetized Plasma Susceptibility Tensor and Faraday Rotation Coefficients}

